Are we living in a depressive society?

### 2024-04-13 outputs/paper/paper.qmd
Update paper.qmd

@fig-ageandtrend-graph illustrates the trends in depressive disorder rates by population subgroup segmented by age, covering the period from May 2020 to March 2024. This graph reveals several key insights about how depressive symptoms have fluctuated across different age groups during and potentially influenced by the ongoing global and societal changes.

@@

@@

@fig-sexandtrend-graph differentiates between the two sex subgroups, highlighting the trends in depressive disorder rates for each:

Female Subgroup: This line consistently shows higher rates of depressive symptoms compared to the male subgroup. The trend line for females exhibits several pronounced peaks which suggest periods of increased stress or exacerbation of symptoms. The higher overall symptom rates in this subgroup might reflect the broader social, economic, and perhaps biological factors that influence mental health disparities between sexes.

Male Subgroup: Although the rates for the male subgroup are generally lower than those for females, the trend line still shows significant fluctuation with similar peaks and troughs, indicating that males are also significantly affected by the same factors that increase depressive symptoms.

@@

@@

The line graph in @fig-raceandtrend-graph shows the depressive disorder rates for several race and ethnicity subgroups, including Hispanic, Caucasian, African American, Asian, and Other (Non-Hispanic, other races and multiple races). Each line represents the trend within a specific subgroup, providing a visual representation of how symptom rates have evolved over the specified period.

Hispanic and African American Subgroups: These lines indicate relatively higher rates of depressive symptoms compared to other groups.

Caucasian Subgroup: This group generally shows lower symptom rates than the Hispanic and African American subgroups but follows a similar trend of fluctuations.

Asian Subgroup: Typically, this line shows the lowest symptom rates among the subgroups.

Other (Non-Hispanic, Other Races and Multiple Races): This category shows a unique trend with variability.

@@

@@

College Graduate or Higher: This subgroup typically shows the lowest rates of depressive symptoms, which might indicate better access to resources, stronger economic stability, or higher awareness and utilization of mental health services.

Some College/Associate's Degree: Individuals in this group exhibit slightly higher rates than those with higher education but still lower than the less educated groups. This might reflect a mid-level access to resources and varying levels of stress related to educational and career expectations.

High School Diploma or GED: This subgroup shows higher rates of depressive symptoms compared to those with more education. The increased rates could be linked to economic challenges, job market limitations, or the stress associated with lower social mobility.

Less Than a High School Diploma: This group consistently shows the highest rates of depressive symptoms, indicating significant vulnerabilities. Factors such as lower economic stability, limited access to healthcare, and higher life stressors likely contribute to these higher rates.

@@

```
```{r}

>>>>

@@

```
@fig-ageandtrend-graph illustrates the trends in depressive disorder rates by population subgroup segmented by age, covering the period from May 2020 to March 2024. This graph reveals several key insights about how depressive symptoms have fluctuated across different age groups during and potentially influenced by the ongoing global and societal changes.

@@

@@

```
@fig-sexandtrend-graph differentiates between the two sex subgroups, highlighting the trends in depressive disorder rates for each:

1. **Female Subgroup:** This line consistently shows higher rates of depressive symptoms compared to the male subgroup. The trend line for females exhibits several pronounced peaks which suggest periods of increased stress or exacerbation of symptoms. The higher overall symptom rates in this subgroup might reflect the broader social, economic, and perhaps biological factors that influence mental health disparities between sexes.

2. **Male Subgroup:** Although the rates for the male subgroup are generally lower than those for females, the trend line still shows significant fluctuation with similar peaks and troughs, indicating that males are also significantly affected by the same factors that increase depressive symptoms.

@@

@@

```
The line graph in @fig-raceandtrend-graph shows the depressive disorder rates for several race and ethnicity subgroups, including Hispanic, Caucasian, African American, Asian, and Other (Non-Hispanic, other races and multiple races). Each line represents the trend within a specific subgroup, providing a visual representation of how symptom rates have evolved over the specified period.

1. **Hispanic and African American Subgroups:** These lines indicate relatively higher rates of depressive symptoms compared to other groups.

2. **Caucasian Subgroup:** This group generally shows lower symptom rates than the Hispanic and African American subgroups but follows a similar trend of fluctuations.

3. **Asian Subgroup:** Typically, this line shows the lowest symptom rates among the subgroups.

4. **Other (Non-Hispanic, Other Races and Multiple Races):** This category shows a unique trend with variability.

@@

@@

1. **College Graduate or Higher:** This subgroup typically shows the lowest rates of depressive symptoms, which might indicate better access to resources, stronger economic stability, or higher awareness and utilization of mental health services.

2. **Some College/Associate's Degree:** Individuals in this group exhibit slightly higher rates than those with higher education but still lower than the less educated groups. This might reflect a mid-level access to resources and varying levels of stress related to educational and career expectations.

3. **High School Diploma or GED:** This subgroup shows higher rates of depressive symptoms compared to those with more education. The increased rates could be linked to economic challenges, job market limitations, or the stress associated with lower social mobility.

4. **Less Than a High School Diploma:** This group consistently shows the highest rates of depressive symptoms, indicating significant vulnerabilities. Factors such as lower economic stability, limited access to healthcare, and higher life stressors likely contribute to these higher rates.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-alonetrend-graph
#| fig-cap: "Adults who usually or always feel lonely"
